\ifx\boi\undefined\input{../templates/words-en.tex}\fi
\def\version{jury-1}
\problemname{Love polygon}
As we all know, TV soap operas with many characters can lead to seriously complicated relationships.
In one TV show, there are $N$ characters. Each character loves exactly one character.

It is possible for a character to initially love themselves. We say that two characters are in a
relationship if and only if they love each other. By shooting someone with a love arrow, it is
possible to change whom that person loves.

Of course, this allows for a particularly nasty type of complication called a ``love polygon''.
We say that 3 or more people are in a ``love polygon'' if the first person loves the second, the
second loves the third and so on, also the last person loves the first.

Recent polling has shown that viewers have grown tired of this drama and would prefer
something more romantic. Therefore, it was decided to shoot some characters with love arrows
so that everyone is in a relationship. What is the least number of love arrows needed to accomplish
that?

\section*{\inputsection}
The first line of the input contains the integer $N$, the number of characters involved.
The next $N$ lines all contain two space-separated names $s$ and $t$, meaning that the character
named $s$ initially loves the character named $t$. Names of the characters are no more than $10$
characters long and consist of lowercase English letters.

\section*{\outputsection}
Output one integer -- the minimum number of love arrows needed to get everyone into a
relationship. If this is not possible, output $-1$.

\section*{\constraints}
\testgroups

\noindent
\begin{tabular}{| l | l | l | l |}
\hline
\group & \points & \limitsname & \additionalconstraints \\ \hline
1     & 21     & $2 \le N \le 20$ & \\ \hline
2     & 25     & $2 \le N \le 100\,000$ & Each person is loved by someone. \\ \hline
3     & 29     & $2 \le N \le 100\,000$ & There are no relationships or ``love polygons''. \\ \hline
4     & 25     & $2 \le N \le 100\,000$ & \\ \hline
\end{tabular}

\section*{\sampleexplanations}
In the first example, there is a unique optimal solution, which consists of shooting \texttt{b}, \texttt{d} and \texttt{f} with love arrows, having them fall in love with \texttt{h}, \texttt{c} and \texttt{e}, respectively.

In the second example (which satisfies the constraints of group 3), there are several optimal solutions.
One of them is to shoot \texttt{a}, \texttt{b} and \texttt{d} with love arrows, and have them fall in love with \texttt{b}, \texttt{a} and \texttt{c}, respectively.

In the third example, we have a love triangle, where no matter how many love arrows we shoot, someone will always be left out.
