\ifx\boi\undefined\input{../templates/words-en.tex}\fi
\def\version{jury-1}
\problemname{Martian DNA}
As you are probably aware, human DNA can be represented as a long string over
an alphabet of size four ({A, C, G, T}), where each symbol represents a
distinct nucleobase (respectively; adenine, cytosine, guanine, and thymine).

For martians, however, things are a bit different; research conducted on the
latest martian captured by NASA revealed that martian DNA consists of a
whopping $K$ distinct nucleobases! Martian DNA may thus be represented as a
string over an alphabet of size $K$.

Now, a certain research group interested in exploiting martian DNA in
artificial intelligence applications has requested to get a single consecutive
piece of a martian DNA string. For $R$ of the nucleobases, they have specified
a minimum quantity of how many they need of that particular nucleobase to be
present in their sample.

Your are interested in finding the shortest substring of the DNA which satisfies their requirements.

\section*{\inputsection}
On the first line, three numbers $N$, $K$, and $R$, respectively denoting the
total length of the martian DNA, the number of distinct nucleobases, and the
number of nucleobases for which the researchers have a minimum quantity
requirement. They obey $1 \le R \le K \le N \le 10^6$.

On the second line follows $N$ space-separated integers, the complete martian
DNA string. The $i$-th of these integers, $D_i$, indicates what nucleobase is
in the $i$-th position of the DNA string. Nucleobases are $0$-indexed, i.e. $0
\leq D_i < K$. Each nucleobase will occur at least once.

Then follows $R$ lines, each containing two integers $B$ and $Q$ representing
respectively a nucleobase and its mimimum required quantity ($0 \le B < K, 1 \le Q \le N$).
No nucleobase will be listed more than once.

\section*{\outputsection}
Output a single integer, the length of the shortest consecutive substring of
the DNA which satisfies the researchers' requirements. If no such substring
exists, output ``\texttt{impossible}''.

\section*{\constraints}
\testgroups

\noindent
\begin{tabular}{| l | l | l |}
\hline
\group & \points & \limitsname \\ \hline
1     & 25     & $1 \le N \le 10^2, R \le 10$ \\ \hline
2     & 25     & $1 \le N \le 4 \cdot 10^3, R \le 10$ \\ \hline
3     & 25     & $1 \le N \le 10^6, R \le 10$ \\ \hline
4     & 25     & $1 \le N \le 10^6$ \\ \hline
\end{tabular}

\section*{\sampleexplanations}
In the first sample, there are three substrings of length $2$ that contain one
each of nucleobases 0 and 1 (namely ``\texttt{0 1}'', ``\texttt{1 0}'' and ``\texttt{0 1}''),
but no substrings of length $1$. Thus the shortest length is $2$.

In the second sample, the (unique) optimal substring is ``\texttt{1 3 2 0 1 2 0}''.

In the third sample, there aren't enough nucleobases of type 0.
